Cross-culture differences in tourists faced with Japanese hospitality: A text mining and rank-biased overlap measure study of satisfaction and dissatisfaction factors in Chinese and Western cultures

### 2020-09-27 1_manuscript/itt-emotion.tex
Removed footnotes, fork for latexdiff, indent party

\usepackage{lineno, hyperref}
% \usepackage[hyperfootnotes=false]{hyperref}
\usepackage{array, pbox}
\usepackage{mathtools}
\usepackage{caption}
\usepackage{graphicx}

@@

% Stick footnotes to bottom of the page
\usepackage[bottom]{footmisc}

@@

In this study, we take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Mainland Chinese tourists posting in \textit{Ctrip}\footnote{\label{ctrip}Ctrip: \href {www.ctrip.com/}{\path{www.ctrip.com/}}} and Western English-speaking tourists populations posting in \textit{TripAdvisor}\footnote{\label{tripadvisor}TripAdvisor: \href {www.tripadvisor.com/}{\path{www.tripadvisor.com/}}}. With this data, we can confirm existing theories about their differences in behavior, as well as perform an exploration of the data to discover factors that could have been overlooked in the past. In order to do this, we use machine learning to automatically classify review sentences as positive or negative opinions of the hotel. We then perform a statistical extraction of the topics that concerns the customers of each population the most.

>>>>

  \usepackage{lineno, hyperref}
  \usepackage{array, pbox}
  \usepackage{mathtools}
  \usepackage{caption}
  \usepackage{graphicx}

@@

@@

  In this study, we take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Mainland Chinese tourists posting in \textit{Ctrip} and Western English-speaking tourists populations posting in \textit{TripAdvisor}. With this data, we can confirm existing theories about their differences in behavior, as well as perform an exploration of the data to discover factors that could have been overlooked in the past. In order to do this, we use machine learning to automatically classify review sentences as positive or negative opinions of the hotel. We then perform a statistical extraction of the topics that concerns the customers of each population the most.
